---
title: "iLosserPackageRepository"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{iLosserPackageRepository}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(iLosserPackageRepository)

#dependencies 

library(ggplot2)
```
  
## TooSnake

TooSnake is a function to transform any type of text to snake case. This process is a widely considered good practice. 

```{r}
# using the first few lines of the bee movie script as an example
TooSnake("There is no way a bee should be able to fly. Its wings are too small to get its fat little body off the ground.")

```

output:
[1] "there_is_no_way_a_bee_should_be_able_to_fly_its_wings_are_too_small_to_get_its_fat_little_body_off_the_ground_"  
  
  
  
## ColSnake
ColSnake is a way of converting column names to Snake case. Useful when needing to use the column name in a data analysis in R.


```{r}
df <- data.frame(
  "First Name" = c("Alice", "Bob", "Charlie"),
  "Last.Name" = c("Smith", "Johnson", "Williams"),
  "User ID" = c(101, 102, 103),
  check.names = FALSE # Allows spaces and special characters in column names
)

# Create a comma-separated string of column names
colnames_first_array <- paste(colnames(df), collapse = ", ")
colnames_colsnake_array <- paste(colnames(ColSnake(df)), collapse = ", ")
paste("The first set of colnames: ", colnames_array)
paste("The ColSnake edited set of colnames: ", colnames_colsnake_array)





```

output:
[1] "The first set of colnames:  First Name, Last.Name, User ID"
[1] "The ColSnake edited set of colnames:  first_name, last_name, user_id"


## theme_GGreen
theme_GGreen is an extension [based on the argitecture] of the ggplot package. This function will effect the colour of the graphs to a classic Snake [the game] type of green.

```{r}
```


```{r}
```

